---
title: "Cyclistic Case Study"
author: "Prince Maynard"
date: "2022-10-29"
output:
  html_document: default
  word_document: default
  pdf_document: default
---
## Simple beginnings

I started simple by loading in the proper packages, reading and assigning the data to an object called "trip_data", and calculating the total amount of casual riders in comparison to members.
```{r}
library(tidyverse)
library(lubridate)
trip_data <- read.csv("C:\\Users\\pgonl\\Downloads\\202209-divvy-publictripdata.csv")
sum(trip_data$member_casual == "casual")
sum(trip_data$member_casual == "member")
```

## First Objects 

Firstly, I decided to create the objects that were to be used in order to find the difference between two columns. Those columns (started_at and ended_at) contained data on the duration of each trip per ride id.
```{r}
Ended <- (trip_data$ended_at)
Started <- (trip_data$started_at)
```

## Finding the difference

Once I finished making the first objects, I then find the difference using those objects and make sure the output comes out as a period. I then created a new object that has the details of the results assigned to it.
```{r}
as_tibble(as.period(difftime(Ended, Started)))
Time_Diff <- as_tibble(as.period(difftime(Ended, Started)))
```